Dynamics of Laterally Propagating Flames in X-ray Bursts

### 2019-09-11 xrb/paper.tex
update table numbers
Updated flame speeds and flame speed plots

\begin{figure*}[t]
\plottwo{flame}{speed}
\caption{\label{fig:flame} Our ``standard'' flame. {\color{red} this should be redone for the boosted flame}}
\end{figure*}

@@

\input{flame_table_1d.tex}

@@

\begin{deluxetable}{lcc}
\tablecaption{\label{table:params} Initial model parameters.}
\tablehead{\colhead{parameter} & \colhead{cool} & \colhead{hot}}
\startdata
$T_\star$       & \multicolumn{2}{c}{$5\times 10^7$~K} \\
$T_\mathrm{hi}$ & $2\times 10^8$~K & $1.2\times 10^9$~K \\
$T_\mathrm{lo}$ & \multicolumn{2}{c}{$10^7$~K} \\
$\rho_\mathrm{int}$ & \multicolumn{2}{c}{$3.43\times 10^6~\gcc$} \\
$\rho_\mathrm{fuel}$\tablenotemark{a} & $2.21\times 10^6~\gcc$ & $1.27\times 10^6~\gcc$ \\
$\rho_\mathrm{cutoff}$ & \multicolumn{2}{c}{$10^{-4}~\gcc$} \\
$g$             & \multicolumn{2}{c}{$-1.5\times 10^{14}~\mathrm{cm~s^{-2}}$} \\
$H_\star$       & \multicolumn{2}{c}{5000~cm} \\
$\delta_\mathrm{atm}$ & \multicolumn{2}{c}{50~cm} \\
$X_\star(\isotm{Fe}{56})\tablenotemark{b}$ & \multicolumn{2}{c}{1.0} \\
$X_\mathrm{atm}(\isotm{He}{4})\tablenotemark{b}$ & \multicolumn{2}{c}{1.0} \\
\enddata
%
\tablenotetext{a}{This is not an input parameter, but instead is
  computed during integration.  We list it here for reference.}
%
\tablenotetext{b}{All other species are taken as 0.}
\end{deluxetable}

@@

\begin{deluxetable}{lcc}
	\tablecaption{\label{table:flame_speeds}Turbulent and laminar flame speeds.}
	\tablehead{\colhead{run} & \colhead{$s_T$ (km s$^{-1}$)} & \colhead{$s_L$ (km s$^{-1}$)}}
	\startdata
	10/10 boost & $9.46 \pm 0.04$  & $1.06 \pm 0.01$ \\
	5/5 boost & $3.97 \pm 0.01$ & $0.56 \pm 0.01$ \\
	iso7 network & $7.66 \pm 0.04$ & $-$ \\
	1000 Hz & $26.1 \pm 0.20$ & $-$ \\
	\enddata
	%
\end{deluxetable}

\begin{figure}[t]
\centering
\plotone{plots/results/speed_10_10.pdf}
\caption{\label{fig:flame_speed}The position of the burning front for the 10/10 flame as a function of time. The dashed line shows a linear least squares fit for $t \gtrsim 10$ ms.}
\end{figure}

>>>>

\begin{figure*}[t]
\plottwo{flame}{speed}
\caption{\label{fig:flame} Our ``standard'' flame.}
\end{figure*}

@@

\iffalse
\input{flame_table_1d.tex}
\fi

@@

\begin{deluxetable}{lcc}
\tablecaption{\label{table:params} Initial model parameters.}
\tablehead{\colhead{parameter} & \colhead{cool} & \colhead{hot}}
\startdata
$T_\star$       & \multicolumn{2}{c}{$10^8$~K} \\
$T_\mathrm{hi}$ & $2\times 10^8$~K & $1.4\times 10^9$~K \\
$T_\mathrm{lo}$ & \multicolumn{2}{c}{$8\times 10^6$~K} \\
$\rho_\mathrm{int}$ & \multicolumn{2}{c}{$3.43\times 10^6~\gcc$} \\
$\rho_\mathrm{fuel}$\tablenotemark{a} & $2.36\times 10^6~\gcc$ & $1.20\times 10^6~\gcc$ \\
$\rho_\mathrm{cutoff}$ & \multicolumn{2}{c}{$10^{-4}~\gcc$} \\
$g$             & \multicolumn{2}{c}{$-1.5\times 10^{14}~\mathrm{cm~s^{-2}}$} \\
$H_\star$       & \multicolumn{2}{c}{2000~cm} \\
$\delta_\mathrm{atm}$ & \multicolumn{2}{c}{50~cm} \\
$X_\star(\isotm{Ni}{56})\tablenotemark{b}$ & \multicolumn{2}{c}{1.0} \\
$X_\mathrm{atm}(\isotm{He}{4})\tablenotemark{b}$ & \multicolumn{2}{c}{1.0} \\
\enddata
%
\tablenotetext{a}{This is not an input parameter, but instead is
  computed during integration.  We list it here for reference.}
%
\tablenotetext{b}{All other species are taken as 0.}
\end{deluxetable}

@@

\begin{deluxetable}{lcc}
	\tablecaption{\label{table:flame_speeds}Turbulent and laminar flame speeds.}
	\tablehead{\colhead{run} & \colhead{$s_T$ (km s$^{-1}$)} & \colhead{$s_L$ (km s$^{-1}$)}}
	\startdata
	10/10 boost & $9.18 \pm 0.03$  & $1.06 \pm 0.01$ \\
	5/5 boost & $4.00 \pm 0.01$ & $0.56 \pm 0.01$ \\
	iso7 network & $7.56 \pm 0.02$ & $-$ \\
	lowres & $9.33 \pm 0.04$ & $-$ \\
	1000 Hz & $18.6 \pm 0.16$ & $-$ \\
	\enddata
	%
\end{deluxetable}

\begin{figure}[t]
\centering
\plotone{plots/results/speedplot_all.pdf}
\caption{\label{fig:flame_speed}The position of the burning front for each simulation run as a function of time. The dashed lines show linear least squares fits for $t \gtrsim 6$ ms.}
\end{figure}
